\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 appendix.tex

RESULT: Cannot find a counterexample in 1500 tests
Testcases were generated randomly.

@@

In a commutativity analysis, J-ReCoVer first tries to compile the example then perform commutativity analysis. If the analysis can not conclude that the example is commutative, J-ReCoVer then runs 1500 randomly generated test cases to try to find a counterexample. If the test cases all pass, then the result will be "unknown".

@@

In this case, one would have to manually fill the types T1 to T4 and the function body, then selects the types from the pull-down menu, as shown in Fig.~\ref{fig:type_select_menu} and Fig.~\ref{fig:selectable_types}.

>>>>

RESULT: Cannot find a counterexample in 500 tests
Testcases were generated randomly.

@@

In a commutativity analysis, J-ReCoVer first tries to compile the example then perform commutativity analysis. If the analysis can not conclude that the example is commutative, J-ReCoVer then runs 500 randomly generated test cases to try to find a counterexample. If the test cases all pass, then the result will be "unknown".

@@

In this case, one would have to manually fill the types T1 to T4 and the function body, then selects the types from the pull-down menu, as shown in Figure~\ref{fig:type_select_menu} and Figure~\ref{fig:selectable_types}.
